### 2021-04-28 yfcc100m/paper/vldb2021/reviewer_response.txt

Reviews: Point addressed
========================================
Reviewer #1

Reviewer #4
    D1. The proposed solution seems to use the functionalities of the existing systems as it is. Authors should provide
    more original ideas or more innovative designs. For example, providing optimizations that specifically target visual
    data or query patterns associated could have been more meaningful to the research communities and convince
    users to replace their customized solution to VDMS.
        - Partially addressed in D3
        - Section 3.1: "...schema of objects(and its properties) before hand. This is a benefit over relational
            databases which require the user to identify how data is divided into
            different tables and determine the relationship between tables."

@@

    D2. Both baselines are similar in architecture, and the evaluation has not effectively highlighted the performance
    gain of other design choices authors made in VDMS, except that the VDMS server process both metadata operation
    and image operation within only one round of communication with clients. For example, benchmarking systems can
    be built to test in isolation the improvement on metadata handling.
        - Should we include metadata only results?

    D3. The paper should detail the types of queries, and image preprocessing it supports, as this being “one of the
    most differentiating aspects” as mentioned by them. And for the selection of operations supported, authors need to
    argue for their decision in the application contexts.
        - In Section 3: "VDMS API also allows users to insert application-defined "Entities", ... In some cases,
            users may need to apply different processing operations to the visual data
            for their application. We chose to support
            specific operations due to their frequent use in ML applications using
            visual data. Common operations supported for both images and videos are
            thresholding, cropping, and resizing. Additional operations such as
            flipping and rotation are supported for images and extracting
            frames by interval is supported for videos.
            In most ML applications, a subset of these operations are included in
            the preprocessing stage of model training and/or inferencing which supports
            majority of the research communities who analyze visual data and may benefit
            from replacing customized solutions with VDMS."

    D4. Data scientists commonly perform data exploration on raw data and interactively curate their datasets for
    downstream tasks like model training. VDMS could design new mechanisms to support interactive analysis, which
    would be beneficial.
        - Out of scope of paper, would require new API to allow interactive analysis
        - Future work?

@@

    D5. In terms of scalability, the paper only shows that VDMS can handle large datasets, yet it is not known how
    VDMS can scale horizontally with more computation resources. For more complex logic of image preprocessing,
    VDMS will suffer from its single server capacity.
    - Sounds more like distributed VDMS to me
    - Any experiements comparing more complex image processing operations?

Reviewer #5
    D1: VDMS is a valuable contribution to Database systems where it takes some first important steps to handle visual data as a first-class citizen instead of considering it a blob of information. However, the description of VDMS is rather short (only 4 pages), and some critical technical details are missing. In particular, what are the technical challenges for supporting ACID properties using the graph model abstraction? Are the solutions analogous to RDBMS’s? Does VDMS also support crash recovery like an RDBMS? What are the key challenges for implementing the new visual object computations?
        - Section 3.2: "...(ACID) properties expected from databases.
            In cases where the system may crash or fail, PMGD has the ability
            to recover to a consistent state without loading its content into memory.
            Unlike existing graph databases that are disk-based, our graph engine
            avoids converting data from a disk-friendly format to an usable format for an application."

    D3: The experiments section seems unnecessarily long, yet missing some important details. All the experiments are performed on images and do not handle videos or feature values at all. For example, video operations may include interval operations or video clip retrieval. Some parts seem redundant, e.g., the description of Figure 9 seems near-identical to that of Figure 8.
        - POssibly remove figure 8 or 9 and use space for either PMGD (D2) or something else

### 2021-04-28 yfcc100m/paper/vldb2021/design.tex
Add crash answer for pmgd in section 3.2 and expanded benefit of no schema in section 3.1

Listing~\ref{addimageandautotag} shows a sample query for inserting
an image, properties associated with the image, and metadata to VDMS.
The metadata, in this case, is the information about the "autotag",
which is provided by the dataset in this specific
\textit{image-search} application.
In this example, the transaction inserts an application-defined "Entity" of
the class "autotag", with the "name" property being \textit{alligator},
inserts an Image with its "latitude" and "longitude",
stores the image as a JPG (VDMS will transcode if needed),
and creates a connection between the Image and the Entity, with a "prob"
property (which indicates the probability of that image
containing an object of type  \textit{alligator}) with a specific value.
This query is performed \textit{transactionally}: either all the image, metadata
and connection are inserted, or none of them are and an error is returned.
Note that no schema needs to be defined in advance.
The Entity of class "autotag", with its properties, are declared and added
at insertion time, without any need to define a schema of objects
(and its properties) before hand.

@@

The Graph Engine used in VDMS is the
\textit{Persistent Memory Graph Database} (PMGD).
PMGD was developed at Intel Labs, and was designed and optimized for
persistent memory technologies like Intel Optane~\cite{IntelXPoint15}, which
promise storage providing nearly the speed of DRAM and the
durability of block-oriented storage.
PMGD is also fully open-sourced \footnote{https://github.com/IntelLabs/pmgd}.
PMGD implements an in-persistent-memory graph database optimized
to run on a platform equipped with persistent memory, but
also provides the option to run on SSD and ext4 filesystem
using OS support to provide transactional guarantees (through \textit{msync}).
PMGD provides a property graph model of data storage with the traditional
atomicity, consistency, isolation, and durability
(ACID) properties expected from databases.
PMGD comes as a C++ library that VDMS uses for implementing its query engine.
Because PMGD already supports most of the graph abstractions we wanted
to see on VDMS API, it was our preferred option.
Also, our internal evaluation shows that PMGD is faster
than other graph databases, including Neo4j\cite{miller2013graph}.
PMGD performance evaluation will be published separately.

>>>>

Listing~\ref{addimageandautotag} shows a sample query for inserting
an image, properties associated with the image, and metadata to VDMS.
The metadata, in this case, is the information about the "autotag",
which is provided by the dataset in this specific
\textit{image-search} application.
In this example, the transaction inserts an application-defined "Entity" of
the class "autotag", with the "name" property being \textit{alligator},
inserts an Image with its "latitude" and "longitude",
stores the image as a JPG (VDMS will transcode if needed),
and creates a connection between the Image and the Entity, with a "prob"
property (which indicates the probability of that image
containing an object of type  \textit{alligator}) with a specific value.
This query is performed \textit{transactionally}: either all the image, metadata
and connection are inserted, or none of them are and an error is returned.
Note that no schema needs to be defined in advance.
The Entity of class "autotag", with its properties, are declared and added
at insertion time, without any need to define a schema of objects
(and its properties) before hand. This is a benefit over relational
databases which require the user to identify how data is divided into
different tables and determine the relationship between tables.

@@

The Graph Engine used in VDMS is the
\textit{Persistent Memory Graph Database} (PMGD).
PMGD was developed at Intel Labs, and was designed and optimized for
persistent memory technologies like Intel Optane~\cite{IntelXPoint15}, which
promise storage providing nearly the speed of DRAM and the
durability of block-oriented storage.
PMGD is also fully open-sourced \footnote{https://github.com/IntelLabs/pmgd}.
PMGD implements an in-persistent-memory graph database optimized
to run on a platform equipped with persistent memory, but
also provides the option to run on SSD and ext4 filesystem
using OS support to provide transactional guarantees (through \textit{msync}).
PMGD provides a property graph model of data storage with the traditional
atomicity, consistency, isolation, and durability
(ACID) properties expected from databases.
In cases where the system may crash or fail, PMGD has the ability
to recover to a consistent state without loading its content into memory.
Unlike existing graph databases that are disk-based, our graph engine
avoids converting data from a disk-friendly format to an usable format for an application.
PMGD comes as a C++ library that VDMS uses for implementing its query engine.
Because PMGD already supports most of the graph abstractions we wanted
to see on VDMS API, it was our preferred option.
Also, our internal evaluation shows that PMGD is faster
than other graph databases, including Neo4j\cite{miller2013graph}.
PMGD performance evaluation will be published separately.
